---
title: "R graphic gallery"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    theme: united
    navbar:
      - { icon: "fa-facebook", href: "https://www.facebook.com/b.byambadorj0212/",align: right, target: blank}
      - { icon: "fa-github", href: "https://github.com/Byambaa212/R_Graphic_Gallery",align: right, target: blank}
---

```{r setup, include=FALSE}
library(flexdashboard)
library(Hmisc) # Small tick marks
library(ggplot2)
library(plotly)
library(tidyverse)
library(extrafont)
library(gridExtra) # Combine ggplot
library(ggthemes)
library(RColorBrewer)
library(gganimate)
library(dygraphs)
library(highcharter)
library(forecast)


# R markdown
# # Multiple pages {data-icon= 'fontawesome.com' }
# ## Column or Row {data-width=} or {data-height}, {.tabset} tabs in 1 chart 
# ### New chart {fig.height=, fig.width=}
# Data
set.seed(3)
data <- data.frame(x = 1:20 + rnorm(20,mean=3),
                  y = 1:20 + rnorm(20,mean=3))
datats <- ts(matrix(rnorm(500), nrow = 500, ncol = 1),
              start = c(1900, 1), frequency = 12)
datafactor <- factor(mtcars$cyl)

ydat=seq(0,95,by=5)
ptypedata <- data.frame(x=1:20,y=ydat)

set.seed(4)
data2 <- data.frame(x = 1:20 + rnorm(20,mean=3),
                  y = 1:20 + rnorm(20,mean=3))

set.seed(3)
dsmall <- diamonds[sample(nrow(diamonds), 1000),]

set.seed(4)
data2 <- data.frame(x = 1:20 + rnorm(20,mean=3),
                  y = 1:20 + rnorm(20,mean=3))

density <- density(diamonds$carat)

lungDeaths <- cbind(mdeaths, fdeaths, ldeaths)

a <- as.data.frame(table(dsmall$cut))
colnames(a) <- c("cut","n")
```

plot {data-icon="fas fa-bars"}
==================================================

Column 1 {.tabset}
--------------------------------------------------
### ScatterPlot
```{r}
# Random data
plot(dsmall$carat,dsmall$price,main="Scatter Plot",col="deeppink4",xlab="",ylab="",pch=16)
```

### BarPlot
```{r}
plot(dsmall$cut,main="Bar Plot",col="deeppink4",xlab="",ylab="")
```


### BoxPlot
```{r}
plot(dsmall$cut,dsmall$carat,main="Box Plot",col="deeppink4",xlab="",ylab="")
```

### TimeSeries
```{r}
plot(datats,main="Time Series",col="deeppink4",xlab="")
```

### Pie chart
```{r}
pie(a$n, labels = c("Fair","Good","Very Good","Premium","Ideal"), border="white",col=brewer.pal(5, "Set1"))
```

### Histogram
```{r}
h <- hist(diamonds$carat, main="",
     xlab="Carat",
     xlim=c(0,3),
     col="deeppink4",
     breaks = 16,
     cex.axis = 1                                 

)
text(h$mids[1:5],h$counts[1:5],labels=h$counts[1:5], adj=c(0.5, 1.4))
text(h$mids[6],h$counts[6],labels=h$counts[6], adj=c(0.5, -0.5))
```

### Density
```{r}
plot(density,col="deeppink4",xlab="",ylab="",main="Density plot")
polygon(density,col="deeppink4",xlab="",ylab="",main="Density plot")
```

### Plot Types
```{r}
attach(ptypedata)
plot(x, y+70, type = "p", main = "Types", ylim= c(0,170),xlab="",ylab="", col=1)
par(new=T)
plot(x, y+60, type = "l", ylim= c(0,170), ann= F,axes=F, col=2)
par(new=T)
plot(x, y+50, type = "b", ylim= c(0,170), ann= F,axes=F, col=3)
par(new=T)
plot(x, y+40, type = "c", ylim= c(0,170), ann= F,axes=F, col=4)
par(new=T)
plot(x, y+30, type = "s", ylim= c(0,170), ann= F,axes=F, col=5)
par(new=T)
plot(x, y+20, type = "o", ylim= c(0,170), ann= F,axes=F, col=6)
par(new=T)
plot(x, y+15, type = "h", ylim= c(0,170), ann= F,axes=F, col=7)
```

Column 2
--------------------------------------------------
### Type Lines
```{r}
reg <- lm(x~y,data=data)
plot1 <- plot(data,
     type="l",
     col="red",                                              # Border color
     col.main = "black",                                     # Title color
     lwd=3,                                                  # Border width 
     main= "Linear Regression line",                         # Title 
     sub= "",                                                # Subtitle
     xlab="X label",                                         # X label
     ylab="Y label",                                         # Y label
     cex.main = 2,                                           # Title size
     cex.lab = 1,                                            # X-axis and Y-axis labels size
     cex.axis = 0.4,                                         # Axis labels size
     ann= T,                                                 # If ann=F delete label names
     axes=F,                                                 # If axes=F remove axis
     tck=0.02,                                               # Interior ticks
     #xaxt="n",                                               # Remove axis tick labels
     #yaxt="n",                                               # Remove axis tick labels
     las=1,                                                  # Rotate axis labels
     xlim=c(0,25),                                           # x limit
     ylim=c(0,25))                                           # y limit
axis(1,at = seq(round(min(x)), round(max(x)), by = 1), labels = 1:20)
axis(2) #,at=0:25)
abline(reg,col="blue",
       lty=2,                                               # plot line style (1-6)
       lwd=3)                                               # plot line width 
text(19,14,"Regression Line")                               # Add text at coordinates
#minor.tick(nx = 3, ny = 3, tick.ratio = 0.5)
legend("bottomright", legend = c("Data", "Linear Regression"), lwd = 3, col = c("red", "blue"),lty = c(1,2))
```

### Type Points
```{r}
group <- ifelse(x < 8 , "1", ifelse(x > 16, "3", "2"))
df <- data.frame(x = x, y = y, group = factor(group))
colors <- c("blue3", "green3", "yellow")
plot(data,
     pch=23,                                                 # Symbol
     col=colors[factor(group, levels = c("1", "2", "3"))],   # Border color
     bg="red1",                                            # Fill color
     col.main = "coral3",                                    # Title color
     col.sub = "blue",                                       # Subtitle color
     col.lab = "brown3",                                     # X and Y-axis labels color
     col.axis = "maroon4",                                   # Tick labels color
     fg = "indianred3",                                      # Box color
     cex=2.5,                                                # Symbol size
     lwd=4,                                                  # Border width 
     main= "Plot including everything",                      # Title 
     sub= "",                                                # Subtitle
     xlab="X label",                                         # X label
     ylab="Y label",                                         # Y label
     cex.main = 2,                                           # Title size
     cex.sub = 1.5,                                          # Subtitle size
     cex.lab = 1.3,                                          # X-axis and Y-axis labels size
     cex.axis = 1.3,                                         # Axis labels size
     ann= T,                                                 # If ann=F delete label names
     axes=T,                                                 # If axes=F remove axis
     tck=0.02,                                               # Interior ticks
     #xaxt="n",                                               # Remove axis tick labels
     #yaxt="n",                                               # Remove axis tick labels
     las=1,                                                  # Rotate axis labels
     xlim=c(0,25),                                           # x limit
     ylim=c(0,25))                                           # y limit
#axis(1,at = seq(round(min(x)), round(max(x)), by = 1), labels = 1:21)
#axis(2) #,at=0:25)
#abline(reg,col="black",
#       lty=2,                                               # plot line style (1-6)
#       lwd=3)                                               # plot line width 
#text(19,14,"Regression Line")                               # Add text at coordinates
#minor.tick(nx = 3, ny = 3, tick.ratio = 0.5)
#legend("bottomright", legend = c("red", "green"), lwd = 3, col = c("red", "green"))
```
 
# ggplot {data-icon="fa-signal"}
## Column 1 {.active .tabset .tabset-fade .tabset-pills}
### BarPlot
```{r}
ggplot(diamonds,aes(x=cut))+geom_bar(fill="deeppink4", color="black", alpha=0.75)+theme_calc()
```

### BarPlot+
```{r}
ggbar5 <- ggplot(diamonds,aes(cut,fill=color))+geom_bar(position = "dodge")+coord_flip()+
  scale_fill_brewer(palette="YlOrRd")
ggplotly(ggbar5)
```

### BoxPlot
```{r}
ggplot(dsmall,aes(y=carat,x=cut))+geom_boxplot(fill="deeppink4", color="black", alpha=0.75)+theme_calc()
```

### BoxPlot+
```{r}
a1 <- ggplot(dsmall, aes(x=cut, y=carat),alpha=0.75) + 
  geom_boxplot(aes(fill=cut)) + 
  scale_fill_brewer(palette="PuRd",name="Quality") +
  transition_states(clarity,
    transition_length = 2,
    state_length = 1) +
  enter_fade() + 
  exit_shrink() +
  ease_aes('sine-in-out')
animate(a1)
```

### Violin
```{r}
ggplot(dsmall,aes(y=carat,x=cut))+
  geom_violin(fill="deeppink4", color="black", alpha=0.75)+theme_calc()
```

### Violin+
```{r}
ggplot(dsmall,aes(y=carat,x=cut))+
  geom_violin(aes(fill=cut),alpha=0.75)+theme_wsj()+
    scale_fill_brewer(palette="PRGn",name="Quality")+
  theme(legend.direction = "vertical",legend.position = "right",
        axis.text.x=element_text(angle=-45, size=12,vjust=0.9))+
  ylim(c(0,3))
```

### Histogram
```{r}
ggplot(dsmall,aes(x=carat))+geom_histogram(fill="deeppink4", color="black", alpha=0.75,binwidth = 0.2)+
  xlim(c(0,3))+theme_calc()
```

### Histogram+
```{r}
hist2 <- ggplot(dsmall,aes(x=carat))+geom_histogram(aes(fill=cut), binwidth = 0.2,
                                                    color="black",alpha=0.75)+
  xlim(c(0,3))+ 
  scale_fill_brewer(palette="BuPu",name="Quality")+
  theme(legend.position = "bottom")+
  theme_fivethirtyeight()
ggplotly(hist2)
```

### Density
```{r}
ggplot(dsmall,aes(x=price))+
      geom_density(aes(fill=color), alpha=0.75)+theme_calc()
```

### Density+
```{r}
options(scipen = 999)
ggplot(dsmall,aes(x=price))+
      geom_density(aes(fill=color), alpha=0.75)+
  theme_gdocs()+
  facet_wrap(vars(color))+
  scale_fill_brewer(palette="Paired",name="Color")+
  theme(axis.text.x=element_text(angle=-45, size=10,vjust=0.1),
        axis.text.y=element_text(angle=0, size=10,vjust=0.1))
```

### Hexbin
```{r}
ggplot(dsmall, aes(x=price, y=carat) ) +
  geom_hex(fill="deeppink4", color="black", alpha=0.75) +theme_calc()
```

### Hexbin+
```{r}
ggplot(dsmall, aes(x=price, y=carat) ) +
  geom_hex() +theme_calc()+scale_fill_gradient(low="lightblue1",high="darkblue",trans="log10")
```

## Column 2 {.active .tabset .tabset-fade .tabset-pills}
### ScatterPlot
```{r}
ggplot1 <- ggplot(dsmall,aes(x=carat,y=price))+geom_point(color="deeppink4")+theme_calc()
ggplot1
```

### +theme economist
```{r}
ggplot2 <- ggplot(dsmall,aes(x=carat,y=price,colour=color))+
  geom_point()+ #geom_point(color="")
  ggtitle("Price by carat")+
  labs(x="Carat",y="Price")+
  theme_economist()+scale_colour_economist(name="Color of \nDiamonds")+
  theme(legend.position = "right") #+theme_classic()
ggplot2
```

### + manual
```{r}
ggplot3 <- ggplot(dsmall,aes(x=carat,y=price,colour=color))+
  geom_point()+ #geom_point(color="")
  ggtitle("Price by \ncarat")+
  labs(x="Carat",y="Price")+
  theme(plot.title = element_text(hjust = 0.45,size=20, face="bold", 
    margin = margin(5, 0, 5, 0), vjust=1, family = "Comic Sans MS", lineheight = 0.7),
    axis.text.x=element_text(angle=0, size=12,vjust=0.9),
    axis.text.y=element_text(angle=0, size=12, vjust=0.5),
    axis.title.x= element_text(color="maroon",size=15),
    axis.title.y= element_text(color="green3",size=15),
    legend.title = element_text(color = "mediumorchid4",size=12,face="bold"),
    legend.key=element_rect(fill='mediumorchid4'),
    panel.background = element_rect(fill = 'gray88'),
    panel.grid.major = element_line(color="darkorchid2",size=0.37),
    panel.grid.minor = element_line(color="maroon"),
    plot.background = element_rect(fill = 'gray80'))+
#  facet_wrap(~color,ncol=2,scales = "free")+
  scale_color_discrete(name="Color of \nDiamonds")+
  ylim(c(0,20000))+ xlim(c(0,3))
# family = "Times New Roman" fonts()
# coord_equal() - axes to be the same
# grid.arrange(ggplot1, plot2, ncol=2) - combine in 1 graph
ggplot3
```

### manual + line
```{r}
ggplot4 <- ggplot(dsmall,aes(x=carat,y=price))+
  geom_point(aes(color="Point Values"),size=1)+ #geom_point(color="")
  stat_smooth(method = "lm",aes(color="Regression Line"))+
  scale_color_manual(name="", values=c("brown2","blue3"))+
  guides(colour = guide_legend(override.aes = list(linetype=c(0,1)
                                                      , shape=c(16, NA))))+
  ggtitle("Price by carat")+
  labs(x="Carat",y="Price")+
  theme(plot.title = element_text(hjust = 0.45,size=20, face="bold", 
    margin = margin(5, 0, 5, 0), vjust=1, family = "Comic Sans MS", lineheight = 0.7),
    axis.text.x=element_text(angle=0, size=12,vjust=0.9),
    axis.text.y=element_text(angle=0, size=12, vjust=0.5),
    axis.title.x= element_text(color="maroon",size=15),
    axis.title.y= element_text(color="green3",size=15),
    panel.background = element_rect(fill = 'gray98'),
    panel.grid.major = element_line(color="green2",size=0.37),
    panel.grid.minor = element_line(color="yellow1",size=0.4),
    plot.background = element_rect(fill = 'gray90'),
    legend.background = element_rect(fill="gray90"),
    # legend.title = element_text(color = "mediumorchid4",size=12,face="bold"),
    legend.key=element_rect(fill='gray74'))+
  ylim(c(0,20000))+ xlim(c(0,3))
 # family = "Times New Roman" fonts()
 # coord_equal() - axes to be the same
ggplot4
```  

### + theme darkunica + manual
```{r}
ggplot5 <- ggplot(dsmall,aes(x=carat,y=price,colour=color))+
  geom_point()+ #geom_point(color="")
  ggtitle("Price by carat")+
  labs(x="Carat",y="Price")+
  theme_hc(style = "darkunica") +
  scale_color_hc(palette="darkunica",name="Color of \nDiamonds")+
theme(plot.title = element_text(hjust = 0.45,size=20, face="bold", 
    margin = margin(5, 0, 5, 0), vjust=1, family = "Comic Sans MS", lineheight = 0.7),
    axis.text.x=element_text(angle=0, size=12,vjust=0.9),
    axis.text.y=element_text(angle=0, size=12, vjust=0.5),
    axis.title.x= element_text(color="maroon",size=15),
    axis.title.y= element_text(color="green3",size=15),
    legend.title = element_text(color = "mediumorchid4",size=12,face="bold"),
    legend.position = "right")+
  geom_text(data=dsmall, aes( x=2.72, y=5500, label="Highest Carat"),
            color="mediumvioletred",size=3.5 , angle=0, fontface="italic")+
  ylim(c(0,20000))+ xlim(c(0,3))
ggplot5
```

### + theme darkunica + manual + animate
```{r}
a2 <- ggplot(dsmall,aes(x=carat,y=price,colour=color))+
  geom_point()+
  ggtitle("Price by carat",subtitle = "Now showing color {closest_state}")+
  labs(x="Carat",y="Price")+
  theme_hc(style = "darkunica") +
  scale_color_hc(palette="darkunica",name="Color of \nDiamonds")+
  theme(plot.title = element_text(hjust = 0.45,size=20, face="bold",color="aquamarine", 
    margin = margin(5, 0, 5, 0), vjust=1, family = "Comic Sans MS", lineheight = 0.7),
    plot.subtitle = element_text(size = 15, color= "deeppink2"),
    axis.text.x=element_text(angle=0, size=12,vjust=0.9),
    axis.text.y=element_text(angle=0, size=12, vjust=0.5),
    axis.title.x= element_text(color="maroon",size=15),
    axis.title.y= element_text(color="green3",size=15),
    legend.title = element_text(color = "mediumorchid4",size=12,face="bold"),
    legend.position = "right")+
  ylim(c(0,20000))+ xlim(c(0,3))+
  transition_states(color,transition_length = 3, state_length = 1) +  
  enter_fade() + 
  exit_shrink()
animate(a2, renderer = gifski_renderer())
```

# plotly {data-icon="fas fa-chart-line"}
## Column 1 {.active .tabset .tabset-fade .tabset-pills}
### Line plot types + Dropdown
```{r}
updatemenus1 <- list(
  list(
    active = -1,
    xanchor = 'left',
    yanchor = "top",
    x = 0.03,
    y = 1,
    buttons = list(
      list(
        label = "Line",
        method = "update",
        args = list(list(visible = c(T, F, F, F, F)),
                    list(title = "Line"))),
      list(
        label = "Dot",
        method = "update",
        args = list(list(visible = c(F, T, F, F, F)),
                    list(title = "Dot"))),
      list(
        label = "Dash",
        method = "update",
        args = list(list(visible = c(F, F, T, F, F)),
                    list(title = "Dash"))),
      list(
        label = "Long Dash",
        method = "update",
        args = list(list(visible = c(F, F, F, T, F)),
                    list(title = "Long Dash"))),
      list(
        label = "Dash Dot",
        method = "update",
        args = list(list(visible = c(F, F, F, F, T)),
                    list(title = "Dash Dot"))),
      list(
        label = "ALL",
        method = "update",
        args = list(list(visible = c(T, T, T, T, T)),
                    list(title = "Line Types")))
      )
  )
)
plot_ly(data2,x=~x) %>% 
  add_lines(y=~y+6, name="Line", line = list(color = 1, width = 3, dash = 'solid')) %>% 
  add_lines(y=~y+4, name="Dot", line = list(color = 2, width = 3, dash = 'dot')) %>% 
  add_lines(y=~y+2, name="Dash", line = list(color = 3, width = 3, dash = 'dash')) %>% 
  add_lines(y=~y, name="Long dash", line = list(color = 4, width = 3, dash = 'longdash')) %>% 
  add_lines(y=~y-2, name="Dash dot", line = list(color = 5, width = 3, dash = 'dashdot')) %>% 
  layout(title="Line types",
         yaxis=list(title=""),
         xaxis=list(title=""),
         showlegend=F,
         updatemenus=updatemenus1)
```

### Line plots modes + buttons
```{r}
updatemenus2 <- list(list(
    active = -1,
    xanchor = 'left',
    yanchor = "top",
    x = 0.03,
    y = 1,
    type= 'buttons',
    buttons = list(
      list(
        label = "Line",
        method = "update",
        args = list(list(visible = c(T, F, F)),
                    list(title = "Line"))),
      list(
        label = "Markers",
        method = "update",
        args = list(list(visible = c(F, T, F)),
                    list(title = "Markers"))),
      list(
        label = "Line+Markers",
        method = "update",
        args = list(list(visible = c(F, F, T)),
                    list(title = "Line+Markers"))),
      list(
        label = "ALL",
        method = "update",
        args = list(list(visible = c(T, T, T)),
                    list(title = "Line plot modes")))
      )
  )
)
plot_ly(data2,x=~x) %>% add_trace(y=~y, name="Line", mode="lines") %>% 
  add_trace(y=~y+2, name="Markers", mode="markers") %>% 
  add_trace(y=~y-2, name="Line+markers", mode="lines+markers") %>% 
    layout(title="Line types",
         yaxis=list(title=""),
         xaxis=list(title=""),
         showlegend=F,
         updatemenus=updatemenus2)
```

### Line interpolation options + Slider
```{r}
data3 <- data.frame(x=1:5,y=c(1,3,2,3,1))
steps <- list(
  list(args = list(list(visible=c(T,F,F,F,F,F))), 
                    label = "Linear", 
                    method = "update", 
                    value = "1"
                    ),
  list(args = list(list(visible=c(F,T,F,F,F,F))), 
                    label = "Spline", 
                    method = "update", 
                    value = "2"
                    ),
  list(args = list(list(visible=c(F,F,T,F,F,F))), 
                    label = "vhv", 
                    method = "update", 
                    value = "3"
                    ),
  list(args = list(list(visible=c(F,F,F,T,F,F))), 
                    label = "hvh", 
                    method = "update", 
                    value = "4"
                    ),
  list(args = list(list(visible=c(F,F,F,F,T,F))), 
                    label = "vh", 
                    method = "update", 
                    value = "5"
                    ),
  list(args = list(list(visible=c(F,F,F,F,F,T))), 
                    label = "hv", 
                    method = "update", 
                    value = "6"
                    ),
  list(args = list(list(visible=c(T,T,T,T,T,T))), 
                    label = "All", 
                    method = "update", 
                    value = "7"
                    )
  )

plot_ly(data3,x=~x) %>% 
  add_lines(y=~y+6, name="Linear", line = list(color = 1, width = 3, shape = "linear")) %>% 
  add_lines(y=~y+4, name="Spline", line = list(color = 2, width = 3, shape = "spline")) %>% 
  add_lines(y=~y+2, name="vhv", line = list(color = 3, width = 3, shape = "vhv")) %>% 
  add_lines(y=~y, name="hvh", line = list(color = 4, width = 3, shape = "hvh")) %>% 
  add_lines(y=~y-2, name="vh", line = list(color = 5, width = 3, shape = "vh")) %>% 
  add_lines(y=~y-4, name="hv", line = list(color = 5, width = 3, shape = "hv")) %>% 
  layout(title="Line Interpolation Options",
         yaxis=list(title=""),
         xaxis=list(title=""),
         sliders = list(
           list(
             active = 1, 
             currentvalue = list(prefix = "Option: "), 
             pad = list(t = 60), 
             steps = steps)))
```


## Column 2 {.active .tabset .tabset-fade .tabset-pills}

### Scatter plot 
```{r}
plot_ly(dsmall,x=~carat,y=~price,color=I("deeppink4"),stroke = I("black"), span = I(0.3),alpha = 0.75)
```

### Scatter plot +
```{r}
l <- list(font = list(
    family = "sans-serif",
    size = 12,
    color = "#000"),
  bgcolor = "#E2E2E2",
  bordercolor = "#FFFFFF",
  borderwidth = 2,
  title=list(text='<b> Color of \nDiamonds </b>'))
attach(dsmall)
plot_ly(dsmall,x=~carat,y=~price, alpha=1,color=~color, colors="RdYlBu",
        symbol=I(18), stroke=I("deeppink4"),span=I(1), size=I(80),
        text=~paste("Price: ",price, "$<br>Color: ", color)) %>% 
  layout(title = "Price by carat",
         xaxis = list(title = "Carat",zeroline=F),
         yaxis = list(title = "Price",zeroline=F),
         legend=l)
```

### Density plot
```{r}
plot_ly(x = ~density$x, y = ~density$y, type = 'scatter', mode = 'lines', fill = 'tozeroy',
        color=I("deeppink4"),stroke = I("black"), span = I(1),alpha = 0.75) %>% 
  layout(xaxis = list(title = 'Carat'),
         yaxis = list(title = 'Density'))
```

### Density plot + 
```{r}
d_fair <- diamonds[which(diamonds$cut=="Fair"),]
d_good <- diamonds[which(diamonds$cut=="Good"),]
d_verygood <- diamonds[which(diamonds$cut=="Very Good"),]
d_premium <- diamonds[which(diamonds$cut=="Premium"),]
d_ideal <- diamonds[which(diamonds$cut=="Ideal"),]

d_fair <- density(d_fair$carat)
d_good <- density(d_good$carat)
d_verygood <- density(d_verygood$carat)
d_premium <- density(d_premium$carat)
d_ideal <- density(d_ideal$carat)

plot_ly(x=~d_fair$x, y=d_fair$y, type='scatter', mode="lines",name = "Fair", fill="tozeroy") %>%
  add_trace(x= ~d_good$x, y= ~d_good$y, name= "Good", fill="tozeroy") %>%
  add_trace(x= ~d_verygood$x, y= ~d_verygood$y, name= "Very Good", fill="tozeroy") %>%
  add_trace(x= ~d_premium$x, y= ~d_premium$y, name= "Premium", fill="tozeroy") %>%
  add_trace(x= ~d_ideal$x, y= ~d_ideal$y, name= "Ideal", fill="tozeroy") %>%
    layout(xaxis = list(title = 'Carat'),
         yaxis = list(title = 'Density'))

```


### BarPlot
```{r}
  plot_ly(diamonds, x=~cut,color=I("deeppink4"),stroke = I("black"), span = I(1),alpha = 0.75) %>%
  add_histogram() %>% 
  group_by(cut) %>% 
    summarise(Count = n()) %>%
  add_text(
    text = ~scales::comma(Count), y = ~Count, 
    textposition = "top middle", 
    cliponaxis = F,
    color=I("black")) %>% 
  layout(showlegend = FALSE)
```

### BarPlot +
```{r}
diamonds %>% 
  count(cut, color) %>% 
  plot_ly(x=~cut,y=~n, color=~color,colors="YlOrRd",type="bar", textposition='auto') %>% 
  layout(xaxis= list(title="Cut"),yaxis = list(title = 'Count'), barmode = 'group') # barmode="stack"
# text=~paste("Price: ",price, "$<br>Color: ", color)
```

### Pie chart
```{r}
diamonds %>% 
  group_by(cut) %>% 
  summarise(Count = n()) %>%
plot_ly(labels= ~cut, values=~Count, type='pie') %>% 
    layout(title = '',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### Pie chart + 
```{r}
colors <- c('rgb(128,133,133)', 'rgb(144,103,167)', 'rgb(210,105,30)', 'rgb(114,147,203)','rgb(211,94,96)')
diamonds %>% 
    group_by(cut) %>% 
    summarise(Count = n()) %>%
plot_ly(labels= ~cut, values=~Count, type='pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#FFFFFF'),
        hoverinfo = 'text',
        text = ~paste('', Count, ''),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 2)),
        showlegend=F) %>% 
  layout(title = '',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
 # layout(showlegend=F)
```

### Boxplot
```{r}
dsmall %>% plot_ly(y=~carat, type="box",color=~cut,colors="YlOrRd")
```

### Histogram
```{r}
plot_ly(dsmall, x=~carat,type = "histogram",
        color=I("deeppink4"),stroke = I("black"), span = I(1),alpha = 0.75)

```

### Histogram +rangeslider
```{r}
plot_ly(dsmall, x=~carat,type = "histogram", color=~cut, colors="BuPu",
        stroke = I("black"), span = I(0.5),alpha = 0.75) %>% 
  layout(barmode="stack", bargap=0.1) %>% 
  rangeslider()

```

### Violin plot
```{r}
dsmall %>% plot_ly(x=~cut,y=~carat, type="violin",
                   color=I("deeppink4"),stroke = I("black"), span = I(1),alpha = 0.75)
```

### Violin plot + 
```{r}
dsmall %>% plot_ly(x=~cut,y=~carat, type="violin", color=~cut, colors="PiYG",
                   stroke = I("black"), span = I(0.1),alpha = 0.75,
                    box = list(visible = T),
    meanline = list(visible = T)) %>% 
  layout(xaxis = list(title = "Cut"), 
         yaxis = list(title = "Carat", zeroline = F))
```

### 3D Density plot
```{r}
dens <- with(diamonds, tapply(price, INDEX = cut, density))
data4 <- data.frame(
  x = unlist(lapply(dens, "[[", "x")),
  y = unlist(lapply(dens, "[[", "y")),
  cut = rep(names(dens), each = length(dens[[1]]$x)))

plot_ly(data4, x = ~x, y = ~y, z = ~cut, type = 'scatter3d', mode = 'lines', color = ~cut)
```

# highcharter {data-icon="fas fa-chart-bar"}
## Column 1 {.active .tabset .tabset-fade .tabset-pills}
### Scatter
```{r}
dsmall %>% 
  hchart('scatter', hcaes(x = carat, y = price), color="#9E2A64") %>% hc_add_theme(hc_theme_smpl()) 
```

### Scatter +
```{r}
dsmall %>% 
  hchart('scatter', hcaes(x = carat, y = price, group = color, size= price), maxSize="3.5%") %>% 
  hc_colors(brewer.pal(6, "RdYlBu"))%>% hc_add_theme(hc_theme_538()) 
```

### Bar plot
```{r}
hchart(diamonds$cut, name = "frequency", color="#9E2A64",borderColor="black",pointWidth = 110,
       showInLegend = F) %>%
  hc_add_theme(hc_theme_elementary()) 
```

### Bar plot +
```{r}
diamonds %>% count(color,cut) %>% hchart("bar", hcaes(x="cut",y="n", group="color", pointWidth=8)) %>% 
  hc_colors(c("#FFFFCC","#FFEDA0","#FED976","#FEB24C","#FD8D3C","#E31A1C","#B10026"))%>%
  hc_add_theme(hc_theme_flat()) 
```

### Tree map
```{r}
diamonds %>% count(cut) %>% hchart("treemap",hcaes(x="cut",value="n",color="n")) %>% 
  hc_colorAxis(stops = color_stops(colors = viridis::inferno(10)))%>% hc_add_theme(hc_theme_ft()) 
```

### Time series
```{r}
lungDeaths %>% hchart()%>% hc_add_theme(hc_theme_bloom()) 
```

### Forecast
```{r}
fc<-forecast(ldeaths,level = 95)
hchart(fc) %>% hc_add_theme(hc_theme_ggplot2())
```

### Pie chart
```{r}
a %>%
  hchart(
    "pie", hcaes(x = cut, y = n),
    name = "")
```

### Area plot
```{r}
diamonds %>% count(cut, color) %>% hchart('areaspline', hcaes(x = cut, y = n, group=color)) %>%
  hc_add_theme(hc_theme_superheroes()) 

```

### Density
```{r}
d_fair <- diamonds[which(diamonds$cut=="Fair"),]
d_good <- diamonds[which(diamonds$cut=="Good"),]
d_verygood <- diamonds[which(diamonds$cut=="Very Good"),]
d_premium <- diamonds[which(diamonds$cut=="Premium"),]
d_ideal <- diamonds[which(diamonds$cut=="Ideal"),]

d_fair <- density(d_fair$carat)
d_good <- density(d_good$carat)
d_verygood <- density(d_verygood$carat)
d_premium <- density(d_premium$carat)
d_ideal <- density(d_ideal$carat)
hchart(
  d_fair, type = "area", 
  color = "#66C2A5", name = "Fair"
  ) %>%
  hc_add_series(
    d_good, type = "area",
    color = "#FC8D62", 
    name = "Good"
    ) %>% 
  hc_add_series(
    d_verygood, type = "area",
    color = "#8DA0CB", 
    name = "Very good"
    ) %>% 
  hc_add_series(
    d_premium, type = "area",
    color = "#E78AC3", 
    name = "Premium"
    ) %>% 
  hc_add_series(
    d_ideal, type = "area",
    color = "#A6D854", 
    name = "Ideal"
    )%>% hc_add_theme(hc_theme_tufte()) 
```

### Boxplot 
```{r}
hcboxplot(
  x = dsmall$carat,
  var = dsmall$cut,
  name = "Box plot", 
  color = "#9E2A64") %>% 
  hc_chart(type = "column") %>% hc_add_theme(hc_theme_alone()) 
```

### Histogram
```{r}
h <- hist(diamonds$carat, main="",
     xlab="Carat",
     xlim=c(0,3),
     col="deeppink4",
     breaks = 30)
hchart(h, name="",showInLegend = F)%>% hc_add_theme(hc_theme_flatdark()) %>% hc_xAxis(title=list(text="carat"))
```

## Column 2 {.tabset}

### Area plot+pie
```{r, fig.width=8}
diamonds %>% count(cut, color) %>% hchart('areaspline', hcaes(x = cut, y = n, group=color)) %>%
  hc_add_theme(hc_theme_google()) %>% 
  hc_add_series(a, "pie", hcaes(x = cut, y = n),
    name = "") %>% 
  hc_plotOptions(
    series = list(
      showInLegend = FALSE,
      pointFormat = "{point.y}%",
      colorByPoint = F
      ),
    pie = list(
      center = c('20%', '20%'),
      size = 150,
      dataLabels = list(enabled = FALSE),
      colorByPoint = T
      )
    ) %>% 
  hc_title(text = "Area plot + pie",   
           style = list(fontWeight = "bold", fontSize = "25px", color="black"),
           align = "center")
```

### 3D bar
```{r, fig.width=8}
highchart() %>% 
  hc_chart(type="column", options3d = list(enabled = TRUE, beta = 15, alpha = 15)) %>% 
  hc_xAxis(categories=a$cut, title = list(text = "Diamond quality"),
           gridLineColor="", gridLineWidth=0) %>% 
  hc_yAxis(title = list(text = "count"), gridLineColor="#606060", gridLineWidth=1,
           plotLines = list(
      list(
        label = list(text = "Highest"),
        color = "#99004C",
        width = 2,
        value = 382)),
      plotBands = list(
      list(
        from = 271,
        to = 382,
        color = hex_to_rgba("red", 0.1),
        label = list(text = "This is a plotBand"),
        # the zIndex is used to put the label text over the grid lines 
        zIndex = 1
      )
    )) %>% 
  hc_add_series(data=a$n, name="freq",showInLegend = F) %>% 
  hc_title(text = "Interactive Bar plot",   
           style = list(fontWeight = "bold", fontSize = "30px", color="White"),
           align = "center") %>% 
  hc_subtitle(text = "Prices of over 50,000 round cut diamonds",align = "center") %>% 
  hc_caption(
    text = "A <b>dataset</b> containing the prices and other attributes of almost 54,000 <i>diamonds</i>.", 
    useHTML = TRUE
  ) %>% 
  hc_add_theme(hc_theme_db()) %>% 
  hc_credits(
    enabled = TRUE, 
    text = "My rpubs",
    href = "https://rpubs.com/byambaa212",
    target= 'blank',
    style = list(fontSize = "10px")) 
```

# dygraph {data-icon="fas fa-chart-area"}
## Column 1 {data-width=350}
### Line plot types 
```{r}
dygraph(ldeaths, main = "All", group = "lung-deaths") %>%
  dySeries("V1", label= "ldeaths",strokeWidth = 2, strokePattern = "dotted",color="#9E2A64") %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4, colors="#9E2A64")
```

### 
```{r}
dygraph(fdeaths, main = "Female", group = "lung-deaths") %>%
  dySeries("V1", label = "fdeaths", strokeWidth = 2, strokePattern = "dashed",color="#9E2A64")%>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4, colors="#9E2A64")
```

### 
```{r}
dygraph(mdeaths, main = "Male", group = "lung-deaths") %>%
  dySeries("V1", label = "mdeaths", strokeWidth = 2, strokePattern = "dotdash",color="#9E2A64")%>% 
  dyOptions(fillGraph = TRUE, fillAlpha = 0.4, colors="#9E2A64")
```

### type+shape+step
```{r, fig.height=12, fig.width=350} 
# pointShape= “dot”, “triangle”, “square”, “diamond”, “pentagon”, “hexagon”, “circle”, “star”, “plus”, “ex”
dygraph(lungDeaths, main = "") %>%
  dySeries("ldeaths", strokeWidth = 2, strokePattern = "dashed", color="") %>% 
  dySeries("mdeaths", drawPoints = T, pointShape = "star", color = "", pointSize = 4) %>%
  dySeries("fdeaths", stepPlot = TRUE, fillGraph = TRUE, color = "") %>%
  dyOptions(colors = brewer.pal(3,"Set1"))
```

## Column 2 
### 
```{r}
dyMultiColumn <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "MultiColumn",
            path = system.file("plotters/multicolumn.js",
                               package = "dygraphs"))
}
dygraph(lungDeaths) %>%
  dyMultiColumn()
```

### 
```{r}
dygraph(lungDeaths, main = "Deaths from Lung Disease (UK)") %>%
  dySeries("ldeaths", label = "Both") %>%
  dySeries("mdeaths", label = "Male") %>%
  dySeries("fdeaths", label = "Female") %>%
  dyOptions(stackedGraph = F, 
            colors=c("#FF8C00","#000066","#800080"),
            includeZero = TRUE, 
            axisLineColor = "#191970",
            axisLabelColor = "#BF3B7D",
            gridLineColor = "#D8BFD8") %>% # colors = brewer.pal(3,"Set1")
  dyHighlight(highlightCircleSize = 5, 
              highlightSeriesBackgroundAlpha = 0.3,
              hideOnMouseOut = T,
              highlightSeriesOpts = list(strokeWidth = 1.5)) %>% 
  dyAxis("x", drawGrid = FALSE) %>%
  dyAxis("y", label = "Deaths", valueRange = c(0,4100)) %>%
  dyRangeSelector(height = 30,dateWindow = c("1975-01-01", "1979-01-01"), strokeColor = "#FFCCE5") %>%
  dyLegend(show = "follow", hideOnMouseOut = T, width=200) %>% # show= "onmouseover","always", "follow"
  dyShading(from = "1975-9-1", to = "1976-2-1", color = "#FFE5CC") %>% 
  dyEvent("1976-2-1", label = "Highest death", labelLoc = "bottom",color = "#696969") %>% 
  dyLimit(330,color="#FF9999",labelLoc = "left",label="Limit") %>% 
  dyUnzoom() %>% 
  dyCrosshair(direction = "vertical")
```




